Illustrating splines using the Titanic dataset

### 2024-06-20 text/05/merging-in-r.Rmd

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- Being updated
- R software
output: html_document
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here's a simple example of how this would work.

>>>>

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- Being updated
- R software
output: html_document
page_update: partial
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here's a simple example of how this would work.

### 2024-06-20 text/06/bayesian-accrual-model.Rmd

---
title: A simple Bayesian model for accrual
author: Steve Simon
source: http://www.pmean.com/06/BayesianAccrualModel.html
date: 2006-11-17
categories:
- Blog post
tags:
- Accrual problems in clinical trials
- Bayesian statistics
output: html_document
---

>>>>

---
title: A simple Bayesian model for accrual
author: Steve Simon
source: http://www.pmean.com/06/BayesianAccrualModel.html
date: 2006-11-17
categories:
- Blog post
tags:
- Accrual problems in clinical trials
- Bayesian statistics
output: html_document
page_update: partial
---

### 2024-06-20 text/11/standard-deviation-ci.Rmd

---
title: Calculating a confidence interval for a standard deviation
author: Steve Simon
date: 2011-07-10
categories:
- Blog post
tags:
- Confidence intervals
output: html_document
---

>>>>

---
title: Calculating a confidence interval for a standard deviation
author: Steve Simon
date: 2011-07-10
categories:
- Blog post
tags:
- Confidence intervals
output: html_document
page_update: complete
---

### 2024-06-20 text/20/non-breaking-spaces.Rmd

---
title: "Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: new
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: new
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
page_update: complete
---

### 2024-06-20 text/22/box-with-no-whiskers.Rmd

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
category: Blog post
tags: Graphical display
source: new
---

>>>>

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
category: Blog post
tags:
- Graphical display
source: new
page_update: complete
---

### 2024-06-20 text/22/different-parameterizations.Rmd
Format change in differentparameterizations.Rmd

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
category: 
- Blog post
tags:
- Analysis of variance
output: html_document
---

@@

```{r}
x0 <- E[ , 1]
x1 <- E[ , 2]
x2 <- E[ , 3]
x3 <- E[ , 4]
beta_E <- coef(lm(y~x0+x1+x2+x3-1))
beta_E
```
### Acknowledgements

>>>>

---
title: "Different parameterizations for one factor ANOVA"
author: "Steve Simon"
source: new
date: "2022-07-06"
category: 
- Blog post
tags:
- Analysis of variance
output: html_document
page_update: complete
---

@@

```{r}
x0 <- E[ , 1]
x1 <- E[ , 2]
x2 <- E[ , 3]
x3 <- E[ , 4]
beta_E <- coef(lm(y~x0+x1+x2+x3-1))
beta_E
```

### Acknowledgements

### 2024-06-20 text/22/mapping-longitude-latitude.Rmd

---
title: "Mapping latitude and longitude"
author: "Steve Simon"
source: new
date: "2022-01-06"
category: 
- Blog post
tags:
- Geocoding
output: html_document
---

>>>>

---
title: "Mapping latitude and longitude"
author: "Steve Simon"
source: new
date: "2022-01-06"
category: 
- Blog post
tags:
- Geocoding
output: html_document
page_update: complete
---

### 2024-06-20 text/22/posix-time.Rmd

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags: Data science
source: new
---

>>>>

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags:
- Data science
source: new
page_update: complete
---

### 2024-06-20 text/23/mcnemar-test.Rmd

---
title: "McNemar's test"
source: "New"
author: Steve Simon
date: 2023-10-31
categories:
- Blog post
tags:
- Measuring benefit and risk
output: html_document
---

>>>>

---
title: "McNemar's test"
source: "New"
author: Steve Simon
date: 2023-10-31
categories:
- Blog post
tags:
- Measuring benefit and risk
output: html_document
page_update: complete
---

### 2024-06-20 text/23/non-standard-evaluation.Rmd

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R software
output: html_document
---

>>>>

---
title: "Non-standard evaluation inside functions and loops"
source: "New"
date: "2023-04-04"
categories:
- Blog post
tags:
- R software
output: html_document
page_update: complete
---

### 2024-06-20 text/23/normal-hedging-hyperprior-part-1.Rmd
More formula updates on hedging hyperprior

---
title: "The hedging hyperprior for the normal distribution: unknown mean, known precision"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

$h(\mu | \mathbf{X}) \propto e^{-(n\tau_F+\tau_0)(\mu-\frac{n \tau_F \bar{X} + \tau_0 \mu_0}{n\tau_F+\tau_0})^2}$

>>>>

---
title: "The hedging hyperprior for the normal distribution: unknown mean, known precision"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---

@@

$h(\mu | \mathbf{X}) \propto
  e^{
    -(n\tau_F+\tau_0)
    (\mu-
      \frac
        {n\tau_F\bar{X}+\tau_0\mu_0}
        {n\tau_F+\tau_0})^2}$

### 2024-06-20 text/23/taylor-series-approximation.Rmd

---
title: "Using a linear Taylor series approximation to estimate rounding error"
source: "New"
author: Steve Simon
date: 2023-09-02
categories:
- Blog post
tags:
- Mathematics
output: html_document
---

>>>>

---
title: "Using a linear Taylor series approximation to estimate rounding error"
source: "New"
author: Steve Simon
date: 2023-09-02
categories:
- Blog post
tags:
- Mathematics
output: html_document
page_update: complete
---

### 2024-06-20 text/23/what-is-a-partial-correlation.Rmd

---
title: "What is a partial correlation?"
source: "New"
author: Steve Simon
date: 2023-12-05
categories:
- Blog post
tags:
- Correlation
- Definitions
output: html_document
---

>>>>

---
title: "What is a partial correlation?"
source: "New"
author: Steve Simon
date: 2023-12-05
categories:
- Blog post
tags:
- Correlation
- Definitions
output: html_document
page_update: complete
---

### 2024-06-20 text/24/encoding-example.Rmd

---
title: Encoding example in R
source: "New"
author: Steve Simon
date: 2024-03-23
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: Encoding example in R
source: "New"
author: Steve Simon
date: 2024-03-23
categories:
- Blog post
tags:
- Data management
output: html_document
page_update: complete
---

### 2024-06-20 text/24/survival-spline.Rmd

---
title: Illustrating splines using the Worcester Heart Attack Study
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Survival analysis
- R programming
output: html_document
---

>>>>

---
title: Illustrating splines using the Worcester Heart Attack Study
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Survival analysis
- R programming
output: html_document
page_update: complete
---

### 2024-06-20 text/24/titanic-spline.Rmd

---
title: Illustrating splines using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Nonlinear regression
- R programming
output: html_document
---

>>>>

---
title: Illustrating splines using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Nonlinear regression
- R programming
output: html_document
page_update: complete
---
